---
title: "DSS Computing Bootcamp Template"
author: "YJ"
date: "8/26/2016"
output: html_document
---

## Load packages

Load the following packages for 

- data wrangling (`dplyr`), and 
- data visualizaiton (`ggplot2`)

```{r message=FALSE}
library(dplyr)
library(ggplot2)
```

## Load data

```{r}
gap <- read.csv("https://bit.ly/gap_data_upd")
```

## Exercises

### Exercise 1

How many observations are in this dataset?

```{r nrow,echo=FALSE}
n = nrow(gap)
```

There are `r n` oberservatiosn in the dataset.

### Exercise 2

Visualize the relationship between GDP and life expectancy for 
countries in Europe in 1952 using a scatter plot.

```{r eu_52}
eu_52 <- gap %>%
  filter(continent == "Europe", year == 1952)
ggplot(data = eu_52, aes(x = gdpPercap, y = lifeExp)) +
  geom_point()  
```

### Exercise 3

Add year 1967 in another color.

```{r}
eu_52_67 <- gap %>%
  filter(continent == "Europe", year %in% c(1952,1967))
ggplot(data = eu_52_67, aes(x = gdpPercap, y = lifeExp,color=factor(eu_52_67$year))) +
  geom_point() 
```


